Viscous Transport in Eroding Porous Media

### 2019-10-07 docs/transport/erosion_transport.tex
making small corrections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Efficiently Applying the Quadrature}
\label{sec:fmm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo[inline]{Bryan is here}
By using the Barycentric quadrature rule, the velocity, shear stress,
and vorticity are computed with an error that is bounded independent of
the target location. However, applied directly, it requires
$\mathcal{O}(N^2)$ operations.  By using a fast summation method, such
as the fast multipole method (FMM)~\cite{gre-rok1987}, this cost can be
reduced to $\mathcal{O}(N)$ operations.  However, the Barycentric
quadrature rules require several $N$-body calculations, and they must be
done for each component of $\bd\Omega$ individually.  The resulting cost
would be prohibitive, so we introduce a hybrid method that combines the
Barycentric quadrature rule and the trapezoid rule.  Note that the
source points of the layer potential is always one of the eroding bodies
or the outer wall, but the target point can either be on another
component of $\bd\Omega$ or it can be in the fluid bulk $\Omega$.

To compute the velocity double-layer potential, we start by applying the
trapezoid rule~\eqref{eqn:trap} accelerated with the FMM.  This
calculation requires $\mathcal{O}(N)$ operations, and we call the
resulting velocity $\vv_\trap(\xx)$.  Since the trapezoid rule is
spectrally accurate, the error of $\vv_\trap(\xx)$ is small for points
sufficiently far from $\bd\Omega$, and this region depends on the number
of discretization points $N_\iin$ and $N_\out$.  However, the trapezoid
rule needs to be replaced with a more accurate quadrature rule for
points that are too close to $\bd\Omega$.  Note that since a point is
typically only close to one or two components of $\bd\Omega$, only the
contribution of these nearby bodies needs to be replaced.  Assuming that
$\xx$ is too close to $\gamma_k$, we first subtract the inaccurate
trapezoid rule approximation of the double-layer potential due to
$\gamma_k$.  Then, the Barycentric quadrature rule is used to compute
the velocity due to $\gamma_k$ with more accuracy.  That is, the final
velocity is
\begin{align}
  \vv(\xx) = \vv_\trap(\xx) - \frac{L_k}{N_k} \sum_{j=1}^{N_\iin} 
    D(\xx,\yy^k_j) \eeta(\yy_j) + \vv^k_\bary(\xx),
  \label{eqn:velocityDecomp}
\end{align}
where $\vv^k_\bary(\xx)$ is the velocity at $\xx$ resulting from
applying the Barycentric quadrature rule to the double-layer potential
due to $\gamma_k$.  This strategy naturally extends to points that are
close to $\Gamma$, and to the scenario when $\xx$ is simultaneously
close to multiple components of $\bd\Omega$.  While the term
$\vv_\trap(\xx)$ in equation~\eqref{eqn:velocityDecomp} is computed for
all target points using the FMM, the other two terms are computed with a
direct summation.  However, these terms are only required for target
points near an eroding body or the outer wall, and these points make up
only a small fraction of the total number of points.

An identical strategy is used to compute the vorticity and the
deformation tensor.  That is, the trapezoid rule is used as a first pass
to form the vorticity and deformation tensor, and then local corrections
are made to replace the inaccuracies of the trapezoid rule.  However,
since the shear stress and vorticity are only computed once per time
step, the trapezoid rule is applied with a direct summation rather than
the FMM.  Relative to the cost of computing the velocity at each
iteration of GMRES with the FMM, the additional once-per-time-step costs
to compute the vorticity and deformation tensor are minimal.

Per grid point, applying the Barycentric quadrature rules dominates the
computational cost. Therefore, it is imperative that we only apply the
Barycentric quadrature when the trapezoid rule is inaccurate.  As a rule
of thumb, the trapezoid rule due to $\gamma_k$ achieves machine epsilon
accuracy if~\cite{bar2014}
\begin{align}
  \label{eqn:TrapCutoff}
  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| > 
    5 \frac{L_k}{N_\iin}.
\end{align}
To avoid checking if all target point $\xx$
satisfy~\eqref{eqn:TrapCutoff}, we make use of the {\thL}
variables~\cite{hou-low-she1994}.  First, given two eroding bodies
$\gamma_i$ and $\gamma_j$ with lengths $L_i$ and $L_j$, and centroids
$\cc_i$ and $\cc_j$, we check if
\begin{align}
  \label{eqn:BodyCutoff}
  \|\cc_i - \cc_j\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi} + 
    \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
\end{align}
where $\alpha_\iin \geq 1$ is a parameter that needs to be determined.
In this manner, rather than using an expensive all-to-all algorithm to
compute the distance between all pairs of discretization points, we
compute the distance between pairs of circle centers.  This criteria
allows us to quickly determine bodies that contain discretization points
where the Barycentric quadrature rule might need to be applied, and the
parameter $\alpha_\iin$ accounts for the fact that the bodies are being
approximated with circles.  Assuming that the two bodies $\gamma_i$ and
$\gamma_j$ satisfy condition~\eqref{eqn:BodyCutoff}, for each point $\xx
\in \gamma_j$, we check if
\begin{align}
  \label{eqn:PointsBodyCutoff}
  \|\xx - \cc_i\| < \frac{L_i}{2\pi}
+ \alpha_\iin \left(\frac{L_i}{N_\iin} \right).
\end{align}
To determine if points on $\gamma_i$ are too close to the outer wall, we
recall that the eroding bodies are all contained in $[-1,1] \times
[-1,1]$, so a target point can only be close to the lines $y = \pm 1$.
Therefore, we first check if
\begin{align}
  \left\|\cc_i - \left[
    \begin{array}{c}
      x_i \\ \pm 1
    \end{array}
    \right]
  \right\| < \frac{L_i}{2 \pi} + \alpha_\out \frac{L_\out}{N_\out},
\end{align}
where $x_i$ is the $x$-coordinate of $\cc_i$. If body $\gamma_i$
satisfies this condition, for each point $\xx=(x,y) \in \gamma_i$, we
apply the Barycentric rule to points that satisfy
\begin{align}
  \label{eqn:PointsWallCutoff}
  |y \pm 1| < \frac{L_i}{2 \pi} +\alpha_\out \frac{L_\out}{N_\out}.
\end{align}
Finally, to determine if a target point $\xx$ in the fluid bulk requires
the Barycentric quadrature rule, we only check
conditions~\eqref{eqn:PointsBodyCutoff}
and~\eqref{eqn:PointsWallCutoff}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time Integration}
\label{sec:time}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We use the time stepping method outlined in Section 3.3 of our previous
work~\cite{qua-moo2018} which we briefly summarize here.  The erosion
rate loses differentiability if the shear stress changes sign, and this
leads to corners developing on $\gamma$ and numerical instabilities.
Therefore, we modify the erosion rate, $V_\nn$ in
equation~\eqref{eqn:erosionModel}, with
\begin{align}
  \Vn = \CE \, \abs{\tau} + \epsilon \langle\abs{\tau}\rangle \left(
    \frac{L}{2\pi} \kappa - 1 \right),
\end{align}
where $\epsilon \ll 1,$ $\langle \cdot \rangle$ is the spatial average,
$L$ is the length of $\gamma$, and $\kappa$ is the curvature of
$\gamma$.  This new term penalizations regions of high curvature, and
the normalization term guarantees that the regularization only changes
the body's shape, but not its total length.

Rather than tracking the $(x,y)$ coordinates, the {\thL} variables are
tracked. In addition, a tangential velocity field is added to each body
so that the discretization points remain equispaced in arclength for all
time.  Additionally, to increase the overall stability of the method, a
narrow Gaussian filter is applied to the erosion rate at each time step.
Time stepping is performed with a second-order Implicit-Explicit
Runge-Kutta method. In particular, the diffusive term corresponding to
the curvature penalization term is discretized implicitly, and all other
terms, which are non-stiff, are treated explicitly.  By using this time
stepping method in conjunction with the Barycentric rule, we stably
evolve the eroding bodies.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{sec:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We now present numerical results on dense packings of bodies eroding in
Stokes flow. Moreover, we analyze transport through the eroded
geometries by examining coarse-grained variables.  Each eroding body is
initially a circle with center $\cc_i$ and radius $r_i$.  The center and
radius are chosen at random, and the body is accepted if it is contained
in $[-1,1] \times [-1,1]$ and is sufficiently separated from all other
bodies.  Since the error of our quadrature method is bounded independent
of the geometry, we consider bodies that are separated by less than 10\%
of an arclength spacing.  The randomized method is repeated until the
initial geometry reaches a desired initial porosity.

@@

In each of the examples, we plot the vorticity in the fluid bulk.  Since
the vorticity and the shear stress agree on surface of the eroding
bodies, the vorticity is a useful method to visualize the erosion rate.
In particular, the rate of erosion is largest in regions where the
magnitude of the vorticity is largest.

The erosion rate loses regularity at stagnation points, which inevitably
leads to corner formation on the bodies.  As described in
Section~\ref{sec:formulation} and our previous work~\cite{qua-moo2018},
we introduce a curvature penalization term and a Gaussian smoothing step
in order to ameliorate corner formation.  For all examples, we use the
smoothing parameters $\eps=15/256$ and $\sigma=10/256$, and the time
step size is $\Delta t = 10^{-4}$.

The common characteristic of each of the experiments is near-contact
between the eroding bodies, outer walls, and streamlines. We use our
numerical methods to describe and visualize the following examples:
\begin{itemize}
  \item{\bf Single Body Close to a Wall}: We consider a single eroding
  body close to the outer wall at $y=-1$.  We impose a shear flow
  centered at $y=-1$ and compare the eroding body's shape to a similar
  experiment of Spagnolie and Mitchell~\cite{mit-spa2017}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A Single Body Close to a Wall}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
First, consider a single eroding body close to a solid wall with the
shear flow
\begin{align}
  \UU(\xx)=\left[
  \begin{array}{c}
    y+1 \\ 0
  \end{array}
  \right],
\end{align}
imposed on the outer wall. Mitchell and Spagnolie~\cite{mit-spa2017}
performed a similar three-dimensional experiment using a second-order
quadrature method.  They initialized the body with its center located
$1.5$ radii above the solid wall.  In two dimensions, the trapezoid rule
is spectrally accurate, and an analogous initial configuration is
possible. However, unless the number of discretization points is
increased, the trapezoid rule becomes obsolete if the eroding body is
initialized closer to the solid wall. Therefore, to simulate erosion
near a solid wall at reasonable levels of discretization, we use our
hybrid method that combines the trapezoid rule and the Barycentric
quadrature rule.

@@

In Figure~\ref{fig:NearWall}, we superimpose the eroding body's shape at
equispaced time steps.  For the three initial configurations, the shear
stress is positive for all time, but varies over several orders of
magnitude.  Therefore, we color the eroding body's boundary with the
logarithm of the shear stress.  Since the shear stress is always
positive, the erosion rate is smooth and corners do not develop, but
interesting shapes form nonetheless.  For instance, in the top half of
the body, there is a sudden increase in the shear stress, and this leads
to a region of high curvature.  This behavior is also present in three
dimensions~\cite{mit-spa2017} (Figure 7(c)).  The biggest difference
between the two- and three-dimensional results is the presence of a
recirculation zone.  In three dimensions, there is no recirculation
between the solid wall and the spherical body~\cite{cha-feu2003}, but
this is possible in two dimensions~\cite{chw-wu1975, hig1985}. To
visualize the flow, we plot the vorticity of the final time step from
Figure~\ref{fig:NearWall} in Figure~\ref{fig:NearWall_vort}.  The
recirculation is present in the region where the vorticity is smallest,
but its size is very small.

\begin{figure}[htbp]
\begin{center}
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width = \textwidth]{./figs/1b_0d4r1h_shear}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width = \textwidth]{./figs/1b_0d4r0d5h_shear}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.38\textwidth}
\includegraphics[width =\textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{}
\end{subfigure}
\caption{\label{fig:NearWall} A single body eroding in a Stokes flow.
The color is the logarithm of the shear stress. Therefore, erosion is
fastest in the red regions (upper half) and slowest in the blue regions
(lower half).  The body is initialized at three different distances from
the lower wall: (a) $h$, (b) $h/2$, and (c) $h/10$.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width = \textwidth]{./figs/1b_0d4r1h_vort}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width = \textwidth]{./figs/1b_0d4r0d5h_vort}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.33\textwidth}
\includegraphics[width = \textwidth]{./figs/1b_0d4r0d1h_vort}
\caption{}
\end{subfigure}
\caption{\label{fig:NearWall_vort} The vorticity of the fluid with a
single body eroding at time t=0.1. The initial distance from the body to
the solid wall are: (a) $h$, (b) $h/2$, and (c) $h/10$.}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Medium Porosity}
\label{sec:Eroding20}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies that are discretized with $N_\iin=256$
points.  The background flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 8. Therefore, $U=1$ once all the bodies have
vanished.  Snapshots of the bodies at four equispaced times are shown in
Figure~\ref{fig:Eroding20vort}.  The color is the vorticity, whose
absolute value is proportional to the erosion rate on solid boundaries.
Initially, several of the eroding bodies are closer to the outer wall
than the $5h$ threshold required for the trapezoid rule to achieve
machine precision.  In particular, the distance between bodies 1, 6, 13,
and 15 and the outer wall is $1.3h$, $2.9h$, $2.8h$, and $1.3h$,
respectively, where $h$ is the arclength spacing of the outer wall
$\Gamma$.  In addition, the distance between several pairs of eroding
bodies, including 1 \& 6, 3 \& 9, 6 \& 8, and 14 \& 18, is too small to
be accurately resolved with the trapezoid rule.  By using the
Barycentric quadrature rule, the interaction between these
nearly-touching bodies can be accurately resolved to the desired
accuracy, and erosion can be simulated until all the bodies have
vanished.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Efficiently Applying the Quadrature}
\label{sec:fmm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
By using the Barycentric quadrature rule, the velocity, shear stress,
and vorticity are computed with an error that is bounded independent of
the target location. However, applied directly, it requires
$\mathcal{O}(N^2)$ operations, where $N$ is the total number of source
and target points.  By using a fast summation method, such as the fast
multipole method (FMM)~\cite{gre-rok1987}, this cost can be reduced to
$\mathcal{O}(N)$ operations.  However, the Barycentric quadrature rules
require several $N$-body calculations.  The resulting cost would be
prohibitive, so we introduce a hybrid method that combines the
Barycentric quadrature rule and an accelerated trapezoid rule.  Note
that the source points of the layer potential is always one of the
eroding bodies or the outer wall, but the target point can either be on
another component of $\bd\Omega$ or it can be in the fluid bulk
$\Omega$.

To compute the velocity double-layer potential, we start by applying the
trapezoid rule~\eqref{eqn:trap} accelerated with the FMM.  This
calculation requires $\mathcal{O}(N)$ operations, and we call the
resulting velocity $\vv_\trap(\xx)$.  Since the trapezoid rule is
spectrally accurate, the error of $\vv_\trap(\xx)$ is small for points
sufficiently far from $\bd\Omega$, and this region depends on the number
of discretization points $N_\iin$ and $N_\out$.  However, the trapezoid
rule needs to be replaced with a more accurate quadrature rule for
points that are too close to $\bd\Omega$.  Note that since a point is
typically only close to one or two components of $\bd\Omega$, only the
contribution of these nearby bodies needs to be replaced.  Assuming that
$\xx$ is too close to $\gamma_k$, we first subtract the inaccurate
trapezoid rule approximation of the double-layer potential due to
$\gamma_k$.  Then, the Barycentric quadrature rule is used to compute
the velocity due to $\gamma_k$ with more accuracy.  Finally, the
velocity at $\xx$ is
\begin{align}
  \vv(\xx) = \vv_\trap(\xx) - \frac{L_k}{N_k} \sum_{j=1}^{N_\iin} 
    D(\xx,\yy^k_j) \eeta(\yy_j) + \vv^k_\bary(\xx),
  \label{eqn:velocityDecomp}
\end{align}
where $\vv^k_\bary(\xx)$ is the velocity at $\xx$ resulting from
applying the Barycentric quadrature rule to the double-layer potential
due to $\gamma_k$.  This strategy naturally extends to points that are
close to $\Gamma$, and to the scenario when $\xx$ is simultaneously
close to multiple components of $\bd\Omega$.  While the term
$\vv_\trap(\xx)$ in equation~\eqref{eqn:velocityDecomp} is computed for
all target points using the FMM, the other two terms are computed with a
direct summation.  However, these terms are only required for target
points near an eroding body or the outer wall, and these points make up
only a small fraction of the total number of points.

An identical strategy is used to compute the vorticity and the
deformation tensor.  That is, the trapezoid rule is used as a first pass
to form the vorticity and deformation tensor, and then local corrections
are made to amend the inaccuracies of the trapezoid rule.  However,
since the shear stress and vorticity are only computed once per time
step, the trapezoid rule is applied with a direct summation rather than
the FMM.  Relative to the cost of computing the velocity at each
iteration of GMRES with the FMM, the additional once-per-time-step costs
to compute the vorticity and deformation tensor are minimal.

Per grid point, applying the Barycentric quadrature rules dominate the
computational cost. Therefore, it is imperative that we only apply the
Barycentric quadrature when the trapezoid rule is inaccurate.  As a rule
of thumb, the trapezoid rule due to $\gamma_k$ achieves machine epsilon
accuracy if~\cite{bar2014}
\begin{align}
  \label{eqn:TrapCutoff}
  d(\xx,\gamma_k) = \inf_{\yy \in \gamma_k} \|\xx - \yy\| > 
    5 \frac{L_k}{N_\iin}.
\end{align}
To avoid checking if all target points $\xx$
satisfy~\eqref{eqn:TrapCutoff}, we make use of the {\thL}
variables~\cite{hou-low-she1994}.  First, given two eroding bodies
$\gamma_i$ and $\gamma_j$ with lengths $L_i$ and $L_j$, and centroids
$\cc_i$ and $\cc_j$, we check if
\begin{align}
  \label{eqn:BodyCutoff}
  \|\cc_i - \cc_j\| < \frac{L_i}{2\pi} + \frac{L_j}{2\pi} + 
    \alpha_\iin \left(\frac{L_i}{N_\iin} + \frac{L_j}{N_\iin} \right),
\end{align}
where $\alpha_\iin \geq 1$ is a parameter that needs to be determined.
In this manner, rather than using an expensive all-to-all algorithm to
compute the distance between all pairs of discretization points, we
compute the distance between pairs of circle centers.  This criteria
allows us to quickly determine bodies that contain discretization points
where the Barycentric quadrature rule might need to be applied, and the
parameter $\alpha_\iin$ accounts for the fact that the bodies are being
approximated with circles.  Assuming that the two bodies $\gamma_i$ and
$\gamma_j$ satisfy condition~\eqref{eqn:BodyCutoff}, for each point $\xx
\in \gamma_j$, we check if
\begin{align}
  \label{eqn:PointsBodyCutoff}
  \|\xx - \cc_i\| < \frac{L_i}{2\pi}
+ \alpha_\iin \left(\frac{L_i}{N_\iin} \right).
\end{align}
To determine if points on $\gamma_i$ are too close to the outer wall, we
recall that the eroding bodies are all contained in $[-1,1] \times
[-1,1]$, so a target point can only be close to the lines $y = \pm 1$.
Therefore, we first check if
\begin{align}
  \left\|\cc_i - \left[
    \begin{array}{c}
      x_i \\ \pm 1
    \end{array}
    \right]
  \right\| < \frac{L_i}{2 \pi} + \alpha_\out \frac{L_\out}{N_\out},
\end{align}
where $x_i$ is the $x$-coordinate of $\cc_i$. If body $\gamma_i$
satisfies this condition, for each point $\xx=(x,y) \in \gamma_i$, we
apply the Barycentric rule to points that satisfy
\begin{align}
  \label{eqn:PointsWallCutoff}
  |y \pm 1| < \frac{L_i}{2 \pi} +\alpha_\out \frac{L_\out}{N_\out}.
\end{align}
Finally, to determine if a target point $\xx$ in the fluid bulk requires
the Barycentric quadrature rule, we only check
conditions~\eqref{eqn:PointsBodyCutoff}
and~\eqref{eqn:PointsWallCutoff}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time Integration}
\label{sec:time}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We use the time stepping method outlined in Section 3.3 of our previous
work~\cite{qua-moo2018} which we briefly summarize here.  The erosion
rate loses differentiability if the shear stress changes sign, and this
leads to corners developing on $\gamma$ and numerical instabilities.
Therefore, we modify the erosion rate, $V_\nn$ in
equation~\eqref{eqn:erosionModel}, with
\begin{align}
  \Vn = \CE \, \abs{\tau} + \epsilon \langle\abs{\tau}\rangle \left(
    \frac{L}{2\pi} \kappa - 1 \right),
\end{align}
where $\epsilon \ll 1,$ $\langle \cdot \rangle$ is the spatial average,
$L$ is the length of $\gamma$, and $\kappa$ is the curvature of
$\gamma$.  This new term penalizations regions of high curvature, and
the normalization term guarantees that the regularization only changes
the body's shape, but not its total length.  Finally, to increase the
overall stability of the method, a narrow Gaussian filter is applied to
the erosion rate at each time step.

Rather than tracking the $(x,y)$ coordinates, the {\thL} coordinates are
tracked. In addition, a tangential velocity field is added to each body
so that the discretization points remain equispaced in arclength for all
time.  Time stepping is performed with a second-order Implicit-Explicit
Runge-Kutta method. In particular, the diffusive term corresponding to
the curvature penalization term is discretized implicitly, and all other
terms, which are non-stiff, are treated explicitly.  By using this time
stepping method in conjunction with the Barycentric rule, we stably
evolve the eroding bodies.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{sec:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We now present numerical results of dense packings of bodies eroding in
Stokes flow. Moreover, we analyze transport through the eroded
geometries by examining coarse-grained variables.  Each eroding body is
initially a circle with center $\cc_i$ and radius $r_i$.  The center and
radius are chosen at random, and the body is accepted if it is contained
in $[-1,1] \times [-1,1]$ and is sufficiently separated from all other
bodies.  Since the error of our quadrature method is bounded independent
of the geometry, we consider bodies that are separated by less than 10\%
of an arclength spacing.  The randomized method is repeated until the
initial geometry reaches a desired initial porosity.

@@

The erosion rate loses regularity at stagnation points, which inevitably
leads to corner formation on the bodies.  As described in
Section~\ref{sec:formulation} and our previous work~\cite{qua-moo2018},
we introduce a curvature penalization term and a Gaussian smoothing step
to ameliorate corner formation.  For all examples, we use the smoothing
parameters $\eps=15/256$ and $\sigma=10/256$, and the time step size is
$\Delta t = 10^{-4}$.

In each of the examples, we plot the vorticity in the fluid bulk.  Since
the vorticity and the shear stress agree on surface of the eroding
bodies, the vorticity is useful to visualize the erosion rate.  In
particular, the rate of erosion is largest in regions where the
magnitude of the vorticity is largest.

The common characteristic of each of the experiments is near-contact
between the eroding bodies, outer walls, and streamlines. We use our
numerical methods to simulate, analyze, and visualize the following
examples:
\begin{itemize}
  \item{\bf Single Body Close to a Wall}: We consider a single eroding
  body close to the outer wall at $y=-1$.  We impose a shear flow
  centered at $y=-1$ and compare the eroding body's shape to a similar
  experiment of Mitchell and Spagnolie~\cite{mit-spa2017}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A Single Body Close to a Wall}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Consider a single eroding body close to a solid wall with the shear flow
\begin{align}
  \UU(\xx)=\left[
  \begin{array}{c}
    y+1 \\ 0
  \end{array}
  \right],
\end{align}
imposed on the outer wall. Mitchell and Spagnolie~\cite{mit-spa2017}
performed a similar three-dimensional experiment using a second-order
quadrature method.  Their initial body is a sphere with its center
located $1.5$ radii above the solid wall.  In two dimensions, the
trapezoid rule is spectrally accurate, and an analogous initial
configuration is possible. However, unless the number of discretization
points is increased, the trapezoid rule becomes obsolete if the eroding
body is initialized too close to the solid wall. Therefore, to simulate
erosion near a solid wall at reasonable levels of discretization, we use
our hybrid method that combines the trapezoid rule and the Barycentric
quadrature rule.

@@

In Figure~\ref{fig:NearWall}, we superimpose the eroding body's shape at
equispaced time steps.  For all three initial configurations, the shear
stress is positive for all time, but varies over several orders of
magnitude.  Therefore, we color the eroding body's boundary with the
logarithm of the shear stress.  Since the shear stress is always
positive, the erosion rate is smooth and corners do not develop, but
interesting shapes form nonetheless.  For instance, in the top half of
the body, there is a sudden increase in the shear stress, and this leads
to a region of high curvature.  This behavior is also present in three
dimensions~\cite{mit-spa2017} (Figure 7(c)).  The biggest difference
between the two- and three-dimensional results is the presence of a
recirculation zone.  In three dimensions, there is no recirculation
between the solid wall and the spherical body~\cite{cha-feu2003}, but
recirculation is possible in two dimensions~\cite{chw-wu1975, hig1985}.
To visualize the flow, we plot the vorticity of the final time step from
Figure~\ref{fig:NearWall} in Figure~\ref{fig:NearWall_vort}.  In these
examples, a small recirculation zone, both in size and magnitude, is
present in the region where the vorticity is smallest

\begin{figure}[htbp]
\begin{center}
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width = \textwidth]{./figs/1b_0d4r1h_shear}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width = \textwidth]{./figs/1b_0d4r0d5h_shear}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.38\textwidth}
\includegraphics[width =\textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{}
\end{subfigure}
\caption{\label{fig:NearWall} A single body eroding in a shearing Stokes
flow.  The color is the logarithm of the shear stress. Therefore,
erosion is fastest in the red regions (upper half) and slowest in the
blue regions (lower half).  The body is initialized at three different
distances from the lower wall: (a) $h$, (b) $h/2$, and (c) $h/10$.}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width = \textwidth]{./figs/1b_0d4r1h_vort}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.3\textwidth}
\includegraphics[width = \textwidth]{./figs/1b_0d4r0d5h_vort}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.33\textwidth}
\includegraphics[width = \textwidth]{./figs/1b_0d4r0d1h_vort}
\caption{}
\end{subfigure}
\caption{\label{fig:NearWall_vort} The vorticity of the fluid with a
single body eroding at time $t=0.1$. The initial distance from the body
to the solid wall are: (a) $h$, (b) $h/2$, and (c) $h/10$.}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 Bodies at a Medium Porosity}
\label{sec:Eroding20}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\todo[inline]{Bryan is here}
We consider 20 eroding bodies that are discretized with $N_\iin=256$
points.  The background flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 8. Therefore, $U=1$ once all the bodies have
vanished.  Snapshots of the bodies at four equispaced times are shown in
Figure~\ref{fig:Eroding20vort}.  The color is the vorticity, whose
absolute value is proportional to the erosion rate on solid boundaries.
Initially, several of the eroding bodies are closer to the outer wall
than the $5h$ threshold required for the trapezoid rule to achieve
machine precision.  In particular, the distance between bodies 1, 6, 13,
and 15 and the outer wall is $1.3h$, $2.9h$, $2.8h$, and $1.3h$,
respectively, where $h$ is the arclength spacing of the outer wall
$\Gamma$.  In addition, the distance between several pairs of eroding
bodies, including 1 \& 6, 3 \& 9, 6 \& 8, and 14 \& 18, is too small to
be accurately resolved with the trapezoid rule.  By using the
Barycentric quadrature rule, the interaction between these
nearly-touching bodies can be accurately resolved to the desired
accuracy, and erosion can be simulated until all the bodies have
vanished.
